Age-related changes in plant growth and traits

### 2016-05-17 scripts/Biology_talk.rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

repro vs. leaf investment for all species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=8, fig.height=8}
win.metafile("figs2/RA_all_spp1.wmf", height=5, width=5)
plot
par(mfrow=c(1,1), cex=1, omi=c(.7,.7,.1,.1), mai=c(.1,.1,.1,0.1)) 
mod <- lm(log(growth_leaf)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
plot((1+repro_inv)~growth_leaf, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),xlab="",ylab="")
#words.top.left.logxy(mod)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5",cex=.7)
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75",cex=.7)
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9",cex=.7)
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95",cex=.7)
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1",cex=.7)
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01",cex=.7)
mtext("reproductive investment (mg)", 2, outer=TRUE,cex=1,line=2)
mtext("leaf investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_canopy.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "RA_leaf_area"
xvar <- "age"

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("canopy species", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_early.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "RA_leaf_area"
xvar <- "age"

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("early reproducers", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_mid.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "RA_leaf_area"
xvar <- "age"

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("mid-age reproducers", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_mid-late.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "RA_leaf_area"
xvar <- "age"

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

RA by age for 4 species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_plot3.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
yvar <- "RA_leaf_area"
xvar <- "age"

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("RA (based on leaf weight only)", 2, outer=TRUE,cex=1,line=1.8)
mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
dev.off()
```

reproductive investment by age for 4 species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_reproinv_by_age.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
xvar <- "age"
yvar <- "repro_inv"

@@

leaf investment by age for 4 species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_leafinv_by_age.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
xvar <- "age"
yvar <- "growth_leaf"

leaf weight by age for 4 species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_leafweight_x_age.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.7,.01,.01), mai=c(.4,.15,.3,0.1)) 
yvar <- "leaf_weight"
xvar <- "age"

reproductive investment vs. leaf investment for 4 species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_LA_tradeoff.wmf", height=7, width=4)
plot

par(mfcol=c(4,1), cex=1, omi=c(.6,.6,.01,.01), mai=c(.4,.1,.3,0.1))

mtext("leaf investment (mg) (log scale)", 2, outer=TRUE,cex=1,line=1)
mtext("reproductive investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
dev.off()
```

##Daniel, don't worry past here

@@

@@

@@

@@

@@

>>>>

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=8, fig.height=8}
win.metafile("figs2/RA_all_spp1.wmf", height=5, width=5)
plot
par(mfrow=c(1,1), cex=1, omi=c(.7,.7,.1,.1), mai=c(.1,.1,.1,0.1)) 
mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),xlab="",ylab="")
words.top.left.logxy(mod)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5",cex=.7)
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75",cex=.7)
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9",cex=.7)
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95",cex=.7)
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1",cex=.7)
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01",cex=.7)
mtext("reproductive investment (mg)", 2, outer=TRUE,cex=1,line=2)
mtext("growth investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=8, fig.height=8}
win.metafile("figs2/RA_all_spp2.wmf", height=5, width=5)
plot
par(mfrow=c(1,1), cex=1, omi=c(.7,.7,.1,.1), mai=c(.1,.1,.1,0.1))  
plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5",cex=.7)
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75",cex=.7)
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9",cex=.7)
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95",cex=.7)
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1",cex=.7)
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01",cex=.7)
mtext("reproductive investment (mg)", 2, outer=TRUE,cex=1,line=2)
mtext("growth investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_reproinv_by_age.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
xvar <- "age"
yvar <- "repro_inv"

@@

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_leafinv_by_age.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
xvar <- "age"
yvar <- "growth_leaf"

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_plot1.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
yvar <- "RA"
xvar <- "age"

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
}
mtext("RA", 2, outer=TRUE,cex=1,line=1.8)
mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
dev.off()
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_plot3.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
yvar <- "RA_leaf_area"
xvar <- "age"

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
}
mtext("RA (based on leaf weight only)", 2, outer=TRUE,cex=1,line=1.8)
mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_leafweight_x_age.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.7,.01,.01), mai=c(.4,.15,.3,0.1)) 
yvar <- "leaf_weight"
xvar <- "age"

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_canopy.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("canopy species", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_early.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("early reproducers", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_mid.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("mid-age reproducers", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_mid-late.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_LA_tradeoff.wmf", height=7, width=4)
plot

par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)

mtext("leaf investment (mg)", 2, outer=TRUE,cex=1,line=2)
mtext("reproductive investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
dev.off()
```

### 2016-05-17 scripts/Growth_figs.rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

>>>>

```{r}
#plot(LMA ~ age,data=subset(SummarySppAge[["mean"]]),col=col.spp(species),pch=16,log="x")

par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "shoot_leaf_area"
xvar <- "growth_leaf"

data <- subset(SummaryInd,age>2&growth_leaf>0)
data <- split(data, data$species)

lmfits <- lapply(data, function(x) lm(log((x[[yvar]])) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age))
}
```

### 2016-05-17 scripts/RA_combined_plots.Rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

pdf("figs2/RA_schedule_plots_3.pdf", height=11.3, width=8)
plot
par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
yvar <- "leaf_area"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

@@

  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="leaf area (midyear)",ylab="total investment (mg)",cex=1.1,
                    col=col.age(data[[spp]]$age),main=spp)
  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="age",ylab="RA",cex=1.1,ylim=c(0,1.4),
                    col=col.age(data[[spp]]$age))
  points(RA_leaf_area~age,data2[[spp]],pch=16)
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="age",ylab="final leaf area",cex=1.1,
                    col=col.age(data[[spp]]$age))
  points(leaf_area~age,data2[[spp]],pch=16)
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="xy",xlab="age",ylab="height",cex=1.1,
                    col=col.age(data[[spp]]$age))
  points(height~age,data2[[spp]],pch=16)
  }
dev.off()
```
SummaryInd$growth_ratio <- SummaryInd$growth_inv /SummaryInd$repro_inv

>>>>

#pdf("figs2/RA_schedule_plots_3.pdf", height=11.3, width=8)
#plot
par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

@@

  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="leaf area (midyear)",ylab="total investment (mg)",cex=1.1,
                    col=col.age(data[[spp]]$age),main=spp)
  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="age",ylab="RA",cex=1.1,ylim=c(0,1.4),
                    col=col.age(data[[spp]]$age))
  points(RA_leaf_area~age,data2[[spp]],pch=16)
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="age",ylab="final leaf area",cex=1.1,
                    col=col.age(data[[spp]]$age))
  points(leaf_area~age,data2[[spp]],pch=16)
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="xy",xlab="age",ylab="height",cex=1.1,
                    col=col.age(data[[spp]]$age))
  points(height~age,data2[[spp]],pch=16)
  }
#dev.off()
```
SummaryInd$growth_ratio <- SummaryInd$growth_inv /SummaryInd$repro_inv
